Application-Level Regression Testing Framework using Jenkins

### 2017-04-11 manuscript/manuscript.tex

\subsection{ssh to a login host}
There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system.

>>>>

\subsection{ssh to a login host}

There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system.
